On the presentation of orthogonal groups over polynomial rings

### 2019-08-06 dl-paper.tex
Minor fix
Proving P1-glueing

\section{Proof of the second part of the injectivity theorem}
\subsection{Presentation of Steinberg groups by homogeneous generators}
\label{sec:presentation}
Let $M\trianglelefteq A$ be an ideal of a commutative ring $A$.
We consider $A[t, t\inv]$ as a $\mathbb{Z}$-graded ring in which $t$ has degree $1$.
We denote by $B = B(A, M)$ the subring $A[t] + M[t\inv] \subseteq A[t, t\inv]$ with the induced grading.
As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=M \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\geq0$. Obviously, $B = A[t]$ in the case $M=0$ and $B = A[t, t\inv]$ in the case $M=A$.

@@

\subsection{Construction of a model for $\St(\Phi, A[X\inv] + M[X])$}
Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise. Let $A$ be a local ring with maximal ideal $M$. As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of the ring of Laurent polynomials $R = A[X, X\inv]$.

@@

\begin{prop} 
For $\Phi$ as in the statement of~\cref{lemma33}.
the operators $T_\alpha$ defined above specify a well-defined action of $\St(\Phi, B)$ on $\overline{V}$.

@@

\begin{theorem}
 Suppose that $\Phi$ is as in the statement of~\cref{lemma33}. Then the map $j_+\colon \St(\Phi, A[X]) \to \St(\Phi, R)$ is injective.

 Suppose, moreover, that $\St(\Phi, B) \to \St(\Phi, R)$ is injective. Then the following square is a pullback square in which all arrows are injective
 \begin{equation} \nonumber
  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R).}
 \end{equation}
\end{theorem}
\begin{proof}

\end{proof}

>>>>

\section{Proof of the main result}
\subsection{Presentation of Steinberg groups by homogeneous generators}
\label{sec:presentation}
Let $M\trianglelefteq A$ be an ideal of a commutative ring $A$.
We consider $A[t, t\inv]$ as a $\mathbb{Z}$-graded ring in which $t$ has degree $1$.
We denote by $B = B(A, M)$ the subring $A[t] + M[t\inv] \subseteq A[t, t\inv]$ with the induced grading.
As an $A$-module $B$ decomposes as $\oplus_{d\in\mathbb Z}B_d$ where $B_d=M \cdot t^d$ for $d<0$, and $B_d=A \cdot t^d$ for $d\geq0$. Obviously, $B = A[t]$ in the case $M=0$ and $B = A[t, t\inv]$ in the case $M=A$.

@@

\subsection{Construction of a model for $\St(\Phi, A[X\inv] + M[X])$}
Throughout this subsection $\Phi$ denotes arbitrary irreducible simply-laced root system of rank $\geq 3$, unless stated otherwise. Let $A$ be a local ring with maximal ideal $M$ and residue field $k$. As in~\cref{firstPart} we denote by $B$ the ring $A[X\inv] + M[X]$ considered as a graded subring of the ring of Laurent polynomials $R = A[X, X\inv]$.

@@

\begin{prop} \label{prop43}
For $\Phi$ as in the statement of~\cref{lemma33}.
the operators $T_\alpha$ defined above specify a well-defined action of $\St(\Phi, B)$ on $\overline{V}$.

@@

\begin{theorem}
 If $\Phi$ is as in the statement of~\cref{lemma33}, then the map $j_-$ is injective.
 If, moreover, $\St(\Phi, A[X]) \to \St(\Phi, B)$ is injective, then the following square is pullback
 \begin{equation} \nonumber
  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R).}
 \end{equation}
\end{theorem}
\begin{proof}
 Let us show that $j_-$ is injective. Set $v_0 = (1, [1], 1) \in \overline{V}$ and suppose $g \in \Ker(j_-)$.
 By~\cref{prop43} holds $v_0 = j_-(g) \cdot v_0 = (g, [g^{-1}], u)$ therefore $g \in G_M^0$ and consequently $g=1$.

 Now suppose $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_-(g_-) = j_+(g_-)$. From~\cref{field-injectivity} it follows that the image $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$. Dividing $g_+$ and $g_-$ by $g_0$ we can achieve
\end{proof}
